---
title: "Findings"
output: html_notebook
---

```{r}
library(tidyverse)
library(countrycode)
library(sqldf)
library(ggmap)
library(leaflet)
```

```{r}
og_data = read_tsv("../data/crunchbase_rounds_20191114.tsv")
funding_situations = read_csv("../data/funding_situations.csv")
industry = read_csv("../data/industry.csv")
locations = read_csv("../data/locations.csv")
country_coord = read_csv("../data/country_coord.csv")
```

```{r}
# adding countries
countries = countrycode(og_data$country_code, 'iso3c', 'country.name')
og_data = cbind(og_data, country_name = countries)
# segmenting funding situations
sqldf("SELECT og_data.*, funding_situations.situation
       FROM og_data INNER JOIN funding_situations
                    ON funding_situations.investment_type = og_data.investment_type") -> og_data
# removing unwanted data
og_data %>% select(-state_code, -raised_amount, -raised_amount_currency_code, -raised_amount_currency_code_1, -post_money_valuation, -investor_names, -post_money_currency_code) -> og_data
# investor ownership calculation
og_data %>% mutate(investor_ownership = raised_amount_usd / post_money_valuation_usd) -> og_data
# fixing up TAN and ROM
og_data$country_name[which(og_data$country_code=="TAN")] = "Fm Tanganyik"
og_data$country_name[which(og_data$country_code=="ROM")] = "Romania"
# for geocode
og_data %>% mutate(ciaco = paste(city, country_name)) -> og_data
# for csv save
og_data %>% mutate(year = as.numeric(substr(announced_on, 1, 4))) -> og_data

sqldf("SELECT og_data.*, locations.lon, locations.lat
       FROM og_data LEFT JOIN locations
                    ON og_data.ciaco == locations.locations") -> og_data
# industry attachment
sqldf("SELECT og_data.*, industry.industry
       FROM og_data INNER JOIN industry
       ON industry.name = company_name") -> og_with_industries
```

## Graced

A time series model
```{r}
graced = og_data %>% filter(situation == "Graced")
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM graced
      GROUP BY year, investment_type") -> pt1
```

```{r}
pt1
```



```{r}
ggplot(pt1, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Graced)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```

Fairly difficult to say how close pre-seeding and non_equity assistance is 

```{r}
pt2 = pt1 %>% filter(investment_type == "pre_seed" | investment_type == "non_equity_assistance")
ggplot(pt2, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + geom_smooth(method="lm", fill = NA) + scale_y_continuous(labels = scales::comma) + ylab("Sum of amount raised") + xlab("Year") + ggtitle("Summation of amount raised per investment type (Graced)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))
```




## Graced Industry

```{r}
og_with_industries %>% filter(situation == "Graced") -> graced_industry
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM graced_industry
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_industry_graced
sum_industry_graced = head(sum_industry_graced, 7)
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount_comparison, industry, investment_type
       FROM graced_industry
       GROUP BY industry, investment_type
       ORDER BY raised_amount_comparison DESC") -> sum_industry_graced_comp
sum_industry_graced_comp
```

```{r}
sum_industry_graced
```


```{r}
sqldf("SELECT A.*
       FROM sum_industry_graced_comp A INNER JOIN sum_industry_graced B
                                       ON A.industry = B.industry") -> sum_industry_graced_comp
sum_industry_graced_comp$industry <- factor(sum_industry_graced_comp$industry, levels = c('biotech', 'mobile', 'software', 'web', 'cleantech', 'medical', 'education'))
```




```{r}
ggplot(sum_industry_graced_comp, aes(fill=investment_type, y=raised_amount_comparison, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (graced)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```
Further pursuit in health consists of grants
technological companies consists of angels

## graced maps

```{r}
sqldf("SELECT SUM(raised_amount_usd) amount_raised, ciaco, lon, lat, country_name
       FROM graced
       GROUP BY ciaco, lon, lat") -> all_region_funding
```


```{r}
NA_funding = all_region_funding %>% filter(country_name == "Canada" | country_name == "United States")
# canada_funding %>% leaflet() %>% addTiles() %>% addMarkers()
```


```{r}
#binpal = colorBin("Reds", domain = 0:max(canada_funding$amount_raised))
#canada_funding %>% 
{my_pal = colorBin(c("#3B5284", "#00FF00"), domain = min(NA_funding$amount_raised):max(NA_funding$amount_raised), bins = 7)

leaflet() %>% addTiles() %>% addCircleMarkers(data = NA_funding, lng = ~lon, lat = ~lat,
                                              color = ~my_pal(amount_raised), opacity = 1) %>% 
  addLegend(data = NA_funding, pal = my_pal, values = ~amount_raised, title = "Summation of amount raised per city")}
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) amount_raised, country_name
       FROM graced
       GROUP BY country_name
       ORDER BY amount_raised DESC") -> all_country_graced
all_country_graced %>% filter(!is.na(country_name)) -> all_country_graced
```

```{r}
all_country_graced
```


```{r}
sqldf("SELECT A.amount_raised, B.*
       FROM country_coord B INNER JOIN all_country_graced A
                          ON A.country_name = B.country_name
       ORDER BY amount_raised DESC") -> sum_country_graced
```

```{r}
top_10_graced = head(sum_country_graced, 10)
bottom_10_graced = tail(sum_country_graced, 20)
```


```{r}
# moment of truth...
leaflet() %>% addTiles() %>% addCircleMarkers(data = top_10_graced, lng = ~lon, lat = ~lat,
                                              opacity = 1)
```

```{r}
bottom_10_graced
```


## crowdfunding and early stages


```{r}
og_data %>% filter(situation == "Crowdfunding and Early Stages") -> cfni
```

```{r}
cfni %>% mutate(year = as.numeric(substr(announced_on, 1, 4))) -> cfni

sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM cfni
      GROUP BY year, investment_type") -> pt1
```

```{r}
pt1 %>% filter(year > 1990) -> pt1
```

```{r}
ggplot(pt1, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Crowdfunding and Early Stages)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```

```{r}
pt1 %>% filter(investment_type != "seed") -> pt2
ggplot(pt2, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + geom_smooth(method="lm", fill = NA) + scale_y_continuous(labels = scales::comma) + ylab("Sum of amount raised") + xlab("Year") + ggtitle("Summation of amount raised per investment type (Crowdfunding and Early Stages)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))
```

## Crowdfunding industry

```{r}
og_with_industries %>% filter(situation == "Crowdfunding and Early Stages") -> graced_industry
```

```{r}
graced_industry %>% filter(investment_type != "seed") -> no_seeding
graced_industry %>% filter(investment_type == "seed") -> with_seeding
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM no_seeding
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_no_seeding
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM with_seeding
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_seeding

sum_no_seeding = head(sum_no_seeding, 7)
my_order = c(sum_seeding$industry)
sum_seeding$industry <- factor(sum_seeding$industry, levels = my_order)


sum_seeding = head(sum_seeding, 7)
```

Next is the comparison amounts only for no seed
```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount_comparison, industry, investment_type
       FROM no_seeding
       GROUP BY industry, investment_type
       ORDER BY raised_amount_comparison DESC") -> sum_industry_ns_comp
```

```{r}
# get the top few
sum_no_seeding
#sum_seeding
```
for no seeding, get the top 10

```{r}
sum_no_seeding
```


```{r}
sqldf("SELECT A.*
       FROM sum_industry_ns_comp A INNER JOIN sum_no_seeding B
                                       ON A.industry = B.industry") -> sum_industry_ns_comp
sum_industry_ns_comp$industry <- factor(sum_industry_ns_comp$industry, levels = c('hospitality', 'finance', 'hardware', 'ecommerce', 'mobile', 'medical', 'real_estate', 'travel'))
```



```{r}
ggplot(sum_industry_ns_comp, aes(fill=investment_type, y=raised_amount_comparison, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (crowdfunding)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```

```{r}
ggplot(sum_seeding, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (seeding)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```

## Series and transitionary funding

```{r}
satf = og_data %>% filter(situation == "Series and transitionary funding")
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, year
      FROM satf
      GROUP BY year") -> pt1
```


```{r}
ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(fill = NA) + ggtitle("Summation of amount raised in Series and Transitionary Funding") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```


```{r}
satf %>% filter(year > 1995) -> satf

sqldf("SELECT AVG(raised_amount_usd) raised_amount, year
      FROM satf
      GROUP BY year") -> pt1

ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(fill = NA) + ggtitle("Averages of amount raised per series and transitionary funding") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Averages of amount raised") + xlab("Year")
```

## series industry

Best industries that have a great sales pitch 

```{r}
series_industry = og_with_industries %>% filter(situation == "Series and transitionary funding")
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM series_industry
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_industry_series
sum_industry_series = head(sum_industry_series, 7)
sum_industry_series


```

```{r}
my_order = sum_industry_series$industry
sum_industry_series$industry <- factor(sum_industry_series$industry, levels = my_order)
ggplot(sum_industry_series, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (Series and Transitionary Funding)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```

## Liquidity Coverages

```{r}
liquid = og_data %>% filter(situation == "Liquidity Coverages")
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM liquid
      GROUP BY year, investment_type") -> pt1
```


```{r}
ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-2500000000, 20000000000)) + geom_smooth(fill = NA) + ggtitle("Summations of debt") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year") + facet_grid(investment_type ~ .) + scale_x_continuous(breaks = scales::pretty_breaks(n = 10))
```


## Liquidity Coverage Industry

```{r}
liquid_industries = og_with_industries %>% filter(situation == "Liquidity Coverages")
```

```{r}
sqldf("SELECT AVG(raised_amount_usd) raised_amount, industry
       FROM liquid_industries
       GROUP BY industry
       ORDER BY raised_amount DESC") -> avg_industry_liquid_1
avg_industry_liquid = head(avg_industry_liquid_1, 7)
```

```{r}
my_order = avg_industry_liquid$industry
avg_industry_liquid$industry <- factor(avg_industry_liquid$industry, levels = my_order)
ggplot(avg_industry_liquid, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 average debt industries") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Average of amount")
```

```{r}
liquid

sqldf("SELECT SUM(raised_amount_usd) raised_amount, country_name
       FROM liquid
       GROUP BY country_name
       ORDER BY raised_amount DESC") -> liquid_countries
top_liquid_countries = head(liquid_countries, 9)
```

```{r}
top_liquid_countries
```

```{r}
my_order = top_liquid_countries$country_name
top_liquid_countries$country_name <- factor(top_liquid_countries$country_name, levels = my_order)
ggplot(top_liquid_countries, aes(y=raised_amount, x=country_name)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 average debt industries") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10), axis.text.x = element_text(angle = 30)) + xlab("Industry") + ylab("Average debt")
```

## Late Game Safety

```{r}
lgs = og_data %>% filter(situation == "Late Game Safety")
lgs
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM lgs
      GROUP BY year, investment_type") -> pt1
pt1 %>% filter(year > 1990)
```

```{r}
ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-5000000, 30000000)) + geom_smooth(fill = NA) + ggtitle("Summation of amount raised per investment type (Graced)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year") + facet_grid(investment_type ~ .) + scale_x_continuous(breaks = scales::pretty_breaks(n = 10))
```
```{r}
ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-5000000000, 30000000000)) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Graced)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```

```{r}
pt2 = pt1 %>% filter(investment_type == "corporate_round")
ggplot(pt2, aes(x = year, y = raised_amount)) + geom_point() + geom_smooth(fill = NA) + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-100000000, 7000000000)) + scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + ylab("Sum of amount raised") + xlab("Year") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10)) + ggtitle("Summation of amount raised per investment type (Corporate Round)")
```


```{r}
pt3 = pt1 %>% filter(investment_type != "corporate_round")
ggplot(pt3, aes(x = year, y = raised_amount)) + geom_point() + geom_smooth(fill = NA) + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-2500000000, 30000000000)) + scale_x_continuous(breaks = scales::pretty_breaks(n = 11)) + ylab("Sum of amount raised") + xlab("Year") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10)) + ggtitle("Summation of amount raised per investment type (Private Equity Round)")
```

2017 seems like a wild year

```{r}
lgs_wo = lgs %>% filter(raised_amount_usd != max(raised_amount_usd))
lgs_wo
lgs_w = lgs %>% filter(raised_amount_usd == max(raised_amount_usd))
lgs_w %>% select(company_name, announced_on, raised_amount_usd)
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM lgs_wo
      GROUP BY year, investment_type") -> pt4
pt5 = pt4 %>% filter(investment_type != "corporate_round")
```

