---
title: "Findings"
output: html_notebook
---

```{r}
library(tidyverse)
library(countrycode)
library(sqldf)
library(ggmap)
library(leaflet)
library(ggrepel)
```

```{r}
og_data = read_tsv("../data/crunchbase_rounds_20191114.tsv")
funding_situations = read_csv("../data/funding_situations.csv")
industry = read_csv("../data/industry.csv")
locations = read_csv("../data/locations.csv")
country_coord = read_csv("../data/country_coord.csv")
```

```{r}
# adding countries
countries = countrycode(og_data$country_code, 'iso3c', 'country.name')
og_data = cbind(og_data, country_name = countries)
# segmenting funding situations
sqldf("SELECT og_data.*, funding_situations.situation
       FROM og_data INNER JOIN funding_situations
                    ON funding_situations.investment_type = og_data.investment_type") -> og_data
# removing unwanted data
og_data %>% select(-state_code, -raised_amount, -raised_amount_currency_code, -raised_amount_currency_code_1, -post_money_valuation, -investor_names, -post_money_currency_code) -> og_data
# investor ownership calculation
og_data %>% mutate(investor_ownership = raised_amount_usd / post_money_valuation_usd) -> og_data
# fixing up TAN and ROM
og_data$country_name[which(og_data$country_code=="TAN")] = "Fm Tanganyik"
og_data$country_name[which(og_data$country_code=="ROM")] = "Romania"
# for geocode
og_data %>% mutate(ciaco = paste(city, country_name)) -> og_data
# for csv save
og_data %>% mutate(year = as.numeric(substr(announced_on, 1, 4))) -> og_data

sqldf("SELECT og_data.*, locations.lon, locations.lat
       FROM og_data LEFT JOIN locations
                    ON og_data.ciaco == locations.locations") -> og_data
# industry attachment
sqldf("SELECT og_data.*, industry.industry
       FROM og_data INNER JOIN industry
       ON industry.name = company_name") -> og_with_industries
```

## Graced

A time series model
```{r}
graced = og_data %>% filter(situation == "Graced")
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM graced
      GROUP BY year, investment_type") -> pt1
```

```{r}
pt1
```



```{r}
ggplot(pt1, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Graced)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```

Fairly difficult to say how close pre-seeding and non_equity assistance is 

```{r}
pt2 = pt1 %>% filter(investment_type == "pre_seed" | investment_type == "non_equity_assistance")
ggplot(pt2, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + geom_smooth(method="lm", fill = NA) + scale_y_continuous(labels = scales::comma) + ylab("Sum of amount raised") + xlab("Year") + ggtitle("Summation of amount raised per investment type (Graced)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))
```




## Graced Industry

```{r}
og_with_industries %>% filter(situation == "Graced") -> graced_industry
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM graced_industry
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_industry_graced
sum_industry_graced = head(sum_industry_graced, 7)
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount_comparison, industry, investment_type
       FROM graced_industry
       GROUP BY industry, investment_type
       ORDER BY raised_amount_comparison DESC") -> sum_industry_graced_comp
sum_industry_graced_comp
```

```{r}
sum_industry_graced
```


```{r}
sqldf("SELECT A.*
       FROM sum_industry_graced_comp A INNER JOIN sum_industry_graced B
                                       ON A.industry = B.industry") -> sum_industry_graced_comp
sum_industry_graced_comp$industry <- factor(sum_industry_graced_comp$industry, levels = c('biotech', 'mobile', 'software', 'web', 'cleantech', 'medical', 'education'))
```




```{r}
ggplot(sum_industry_graced_comp, aes(fill=investment_type, y=raised_amount_comparison, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (graced)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```
Further pursuit in health consists of grants
technological companies consists of angels

## graced maps

```{r}
sqldf("SELECT SUM(raised_amount_usd) amount_raised, ciaco, lon, lat, country_name
       FROM graced
       GROUP BY ciaco, lon, lat") -> all_region_funding
```

### Starting point
```{r}
#binpal = colorBin("Reds", domain = 0:max(canada_funding$amount_raised))
#canada_funding %>% 
{NA_funding = all_region_funding %>% filter(country_name == "Canada" | country_name == "United States")
# canada_funding %>% leaflet() %>% addTiles() %>% addMarkers()
  
my_pal = colorBin(c("#FDBCB4", "#333399"), domain = 1:5, bins = 4)
pspal = c(my_pal(1), my_pal(2), my_pal(3), my_pal(4))

the_min = min(NA_funding$amount_raised)
range = max(NA_funding$amount_raised) - the_min
interval = range / 4

start_rng = c(the_min, the_min + floor(interval*1) + 1, the_min + floor(interval*2) + 1, the_min + floor(interval*3) + 1)

end_rng = c(the_min + floor(interval*1), the_min + floor(interval*2), the_min + floor(interval*3),max(NA_funding$amount_raised))

alt_pal = data.frame(start_rng, end_rng, pspal)
alt_pal = alt_pal %>% mutate(start_rng = as.numeric(start_rng), end_rng = as.numeric(end_rng))
alt_pal %>% mutate(range_str = paste(as.character(start_rng), "-", as.character(end_rng))) -> alt_pal

sqldf("SELECT NA_funding.*, alt_pal.*
       FROM NA_funding INNER JOIN alt_pal
                       ON NA_funding.amount_raised >= alt_pal.start_rng
                       AND NA_funding.amount_raised <= alt_pal.end_rng") -> with_pals

leaflet() %>% addTiles() %>% addCircleMarkers(data = NA_funding, lng = ~lon, lat = ~lat,
                                              color = ~my_pal(amount_raised), opacity = 1) %>% 
  addLegend(data = NA_funding, pal = my_pal, values = ~amount_raised, title = "Summation of amount raised per city")}
```

### final_product
```{r}
my_pal = colorBin(c("#FDBCB4", "#333399", "#121238"), domain = 1:6, bins = 5)
pspal = c(my_pal(1), my_pal(2), my_pal(3), my_pal(4), my_pal(5))

the_min = 0
range = max(all_region_funding$amount_raised) - the_min

start_rng = c(0, 1000001, 100000001, 1000000001, 10000000001)
end_rng = c(1000000, 100000000, 1000000000, 10000000000, max(all_region_funding$amount_raised))
alt_pal = data.frame(start_rng, end_rng, pspal)
alt_pal = alt_pal %>% mutate(start_rng = as.numeric(start_rng), end_rng = as.numeric(end_rng))
labels = c("0 - 1,000,000", "1,000,001 - 10,000,000", "10,000,001 - 100,000,000", "100,000,001 - 1,000,000,000", "1,000,000,000+")

alt_pal %>% mutate(range_str = labels) -> alt_pal

sqldf("SELECT all_region_funding.*, alt_pal.*
       FROM all_region_funding INNER JOIN alt_pal
                       ON all_region_funding.amount_raised >= alt_pal.start_rng
                       AND all_region_funding.amount_raised <= alt_pal.end_rng") -> with_pals
```

```{r}
leaflet() %>% addProviderTiles(providers$Stamen.TonerLite) %>% addCircleMarkers(data = with_pals, lng = ~lon, lat = ~lat,
                                               color = ~pspal, opacity = 0.65, radius = 10) %>% 
  addLegend(data = with_pals, colors = pspal, title = "Summation of amount raised per city (Graced)", labels = alt_pal$range_str)
```
#### Assessment
```{r}
with_pals %>% filter(country_name == "Canada") %>% filter(amount_raised == max(amount_raised))
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) amount_raised, country_name
       FROM graced
       GROUP BY country_name
       ORDER BY amount_raised DESC") -> all_country_graced
all_country_graced %>% filter(!is.na(country_name)) -> all_country_graced
```

## crowdfunding and early stages


```{r}
og_data %>% filter(situation == "Crowdfunding and Early Stages") -> cfni
```

```{r}
cfni %>% mutate(year = as.numeric(substr(announced_on, 1, 4))) -> cfni

sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM cfni
      GROUP BY year, investment_type") -> pt1
```

```{r}
pt1 %>% filter(year > 1990) -> pt1
```

```{r}
ggplot(pt1, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Crowdfunding and Early Stages)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```

```{r}
pt1 %>% filter(investment_type != "seed") -> pt2
ggplot(pt2, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + geom_smooth(method="lm", fill = NA) + scale_y_continuous(labels = scales::comma) + ylab("Sum of amount raised") + xlab("Year") + ggtitle("Summation of amount raised per investment type (Crowdfunding and Early Stages)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))
```

## Crowdfunding industry

```{r}
og_with_industries %>% filter(situation == "Crowdfunding and Early Stages") -> graced_industry
```

```{r}
graced_industry %>% filter(investment_type != "seed") -> no_seeding
graced_industry %>% filter(investment_type == "seed") -> with_seeding
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM no_seeding
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_no_seeding
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM with_seeding
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_seeding

sum_no_seeding = head(sum_no_seeding, 7)
my_order = c(sum_seeding$industry)
sum_seeding$industry <- factor(sum_seeding$industry, levels = my_order)


sum_seeding = head(sum_seeding, 7)
```

Next is the comparison amounts only for no seed
```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount_comparison, industry, investment_type
       FROM no_seeding
       GROUP BY industry, investment_type
       ORDER BY raised_amount_comparison DESC") -> sum_industry_ns_comp
```

```{r}
# get the top few
sum_no_seeding
#sum_seeding
```
for no seeding, get the top 10

```{r}
sum_no_seeding
```


```{r}
sqldf("SELECT A.*
       FROM sum_industry_ns_comp A INNER JOIN sum_no_seeding B
                                       ON A.industry = B.industry") -> sum_industry_ns_comp
sum_industry_ns_comp$industry <- factor(sum_industry_ns_comp$industry, levels = c('hospitality', 'finance', 'hardware', 'ecommerce', 'mobile', 'medical', 'real_estate', 'travel'))
```



```{r}
ggplot(sum_industry_ns_comp, aes(fill=investment_type, y=raised_amount_comparison, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (crowdfunding)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```

```{r}
ggplot(sum_seeding, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (seeding)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```

## Series and transitionary funding

```{r}
satf = og_data %>% filter(situation == "Series and transitionary funding")
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, year
      FROM satf
      GROUP BY year") -> pt1
```


```{r}
ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(fill = NA) + ggtitle("Summation of amount raised in Series and Transitionary Funding") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```


```{r}
satf %>% filter(year > 1995) -> satf

sqldf("SELECT AVG(raised_amount_usd) raised_amount, year
      FROM satf
      GROUP BY year") -> pt1

ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(fill = NA) + ggtitle("Averages of amount raised per series and transitionary funding") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Averages of amount raised") + xlab("Year")
```

## series industry

Best industries that have a great sales pitch 

```{r}
series_industry = og_with_industries %>% filter(situation == "Series and transitionary funding")
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM series_industry
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_industry_series
sum_industry_series = head(sum_industry_series, 7)
sum_industry_series


```

```{r}
my_order = sum_industry_series$industry
sum_industry_series$industry <- factor(sum_industry_series$industry, levels = my_order)
ggplot(sum_industry_series, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries raised by investment type (Series and Transitionary Funding)") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```

## Liquidity Coverages

```{r}
liquid = og_data %>% filter(situation == "Liquidity Coverages")
```


```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM liquid
      GROUP BY year, investment_type") -> pt1
```


```{r}
ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-2500000000, 20000000000)) + geom_smooth(fill = NA) + ggtitle("Summations of debt") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year") + facet_grid(investment_type ~ .) + scale_x_continuous(breaks = scales::pretty_breaks(n = 10))
```


## Liquidity Coverage Industry

```{r}
liquid_industries = og_with_industries %>% filter(situation == "Liquidity Coverages")
```

```{r}
sqldf("SELECT AVG(raised_amount_usd) raised_amount, industry
       FROM liquid_industries
       GROUP BY industry
       ORDER BY raised_amount DESC") -> avg_industry_liquid_1
avg_industry_liquid = head(avg_industry_liquid_1, 7)
```

```{r}
my_order = avg_industry_liquid$industry
avg_industry_liquid$industry <- factor(avg_industry_liquid$industry, levels = my_order)
ggplot(avg_industry_liquid, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 average debt industries") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Average of amount")
```

```{r}
liquid

sqldf("SELECT SUM(raised_amount_usd) raised_amount, country_name
       FROM liquid
       GROUP BY country_name
       ORDER BY raised_amount DESC") -> liquid_countries
top_liquid_countries = head(liquid_countries, 9)
```

```{r}
top_liquid_countries
```

```{r}
my_order = top_liquid_countries$country_name
top_liquid_countries$country_name <- factor(top_liquid_countries$country_name, levels = my_order)
ggplot(top_liquid_countries, aes(y=raised_amount, x=country_name)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 average debt industries") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10), axis.text.x = element_text(angle = 30)) + xlab("Industry") + ylab("Average debt")
```

## Late Game Safety

```{r}
lgs = og_data %>% filter(situation == "Late Game Safety")
lgs
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM lgs
      GROUP BY year, investment_type") -> pt1
pt1 %>% filter(year > 1990)
```

```{r}
ggplot(pt1, aes(x = year, y = raised_amount)) + geom_point() + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-5000000000, 30000000000)) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Late Game Safety)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year") + facet_grid(investment_type ~ .)
```

```{r}
pt2 = pt1 %>% filter(investment_type == "corporate_round")
ggplot(pt2, aes(x = year, y = raised_amount)) + geom_point() + geom_smooth(fill = NA) + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-100000000, 7000000000)) + scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) + ylab("Sum of amount raised") + xlab("Year") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10)) + ggtitle("Summation of amount raised per investment type (Corporate Round)")
```


```{r}
pt3 = pt1 %>% filter(investment_type != "corporate_round")
ggplot(pt3, aes(x = year, y = raised_amount)) + geom_point() + geom_smooth(fill = NA) + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-2500000000, 30000000000)) + scale_x_continuous(breaks = scales::pretty_breaks(n = 11)) + ylab("Sum of amount raised") + xlab("Year") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10)) + ggtitle("Summation of amount raised per investment type (Private Equity Round)")
```

2017 seems like a wild year

```{r}
lgs_wo = lgs %>% filter(raised_amount_usd != max(raised_amount_usd))
lgs_wo
lgs_w = lgs %>% filter(raised_amount_usd == max(raised_amount_usd))
lgs_w %>% select(company_name, announced_on, raised_amount_usd)
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM lgs_wo
      GROUP BY year, investment_type") -> pt4
pt5 = pt4 %>% filter(investment_type != "corporate_round")
```

## Publicity and Beyond

```{r}
pab = og_data %>% filter(situation == "Publicity and Beyond")
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, investment_type, year
      FROM pab
      GROUP BY year, investment_type") -> pt1
pt1 = pt1 %>% filter(year != 2019)
```

```{r}
ggplot(pt1, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + scale_y_continuous(labels = scales::comma) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Publicity and Beyond)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year")
```

We may want to look at post_ipo equity and ICO separately


```{r}
pt2 = pt1 %>% filter(investment_type != "post_ipo_equity") 
ggplot(pt2, aes(x = year, y = raised_amount, color = investment_type)) + geom_point() + scale_y_continuous(labels = scales::comma, expand = c(0, 0), limits = c(-250000000, 1500000000)) + geom_smooth(method = "lm", fill = NA) + ggtitle("Summation of amount raised per investment type (Publicity and Beyond)") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.5, size = 10))  + ylab("Sum of amount raised") + xlab("Year") +scale_x_continuous(breaks = scales::pretty_breaks(n = 9))
```

```{r}
pab %>% filter(year == 2018 & investment_type == "post_ipo_secondary")
```

## Publicity Industry
```{r}
og_with_industries %>% filter(situation == "Publicity and Beyond") -> pub_industry
```

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, industry
       FROM pub_industry
       GROUP BY industry
       ORDER BY raised_amount DESC") -> sum_industry_pub_all
sum_industry_pub = head(sum_industry_pub_all, 7)
```

```{r}
sum_industry_pub_all
```


```{r}
my_order = sum_industry_pub$industry
sum_industry_pub$industry <- factor(sum_industry_pub$industry, levels = my_order)
ggplot(sum_industry_pub, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries within the public by total amount raised") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Summation of amount raised")
```

```{r}
sqldf("SELECT AVG(raised_amount_usd) raised_amount, industry
       FROM pub_industry
       GROUP BY industry
       ORDER BY raised_amount DESC") -> avg_industry_pub_all
avg_industry_pub = head(avg_industry_pub_all, 7)

my_order = avg_industry_pub$industry
avg_industry_pub$industry <- factor(avg_industry_pub$industry, levels = my_order)
ggplot(avg_industry_pub, aes(y=raised_amount, x=industry)) + 
    geom_bar(position="stack", stat="identity") + ggtitle("Top 7 industries within the public by average") +  scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10)) + xlab("Industry") + ylab("Average of amount raised")
```


## Distributions of funding, not including industry

pie graph by situation

```{r}
sqldf("SELECT SUM(raised_amount_usd) raised_amount, situation
       FROM og_data
       GROUP BY situation") -> for_pie
```

```{r}
for_pie
```

```{r}
for_pie
for_pie %>%  mutate(Situation = paste(situation, "-", round(raised_amount * 100 / sum(raised_amount), 2), "%")) -> for_pie

ggplot(for_pie, aes(x = "", y = raised_amount, fill = Situation)) + geom_bar(width=1, stat="identity") + coord_polar("y", start = 0) + scale_fill_brewer(palette="Blues") +
  theme_minimal() + ylab("Proportion of amount raised") + ggtitle("Situation and amount raised") + theme(text = element_text(size = 15), plot.title=element_text(hjust = 0.8, size = 17.5), axis.ticks = element_blank(), panel.grid  = element_blank(), axis.text = element_blank()) + xlab("")
```

Taking a look at averages

```{r}
sqldf("SELECT avg(raised_amount_usd) raised_amount, situation
       FROM og_data
       GROUP BY situation
       ORDER BY raised_amount DESC") -> for_comp
```

```{r}
for_comp
```

```{r}
my_order = for_comp$situation
for_comp$situation <- factor(for_comp$situation, levels = my_order)
ggplot(for_comp, aes(y=raised_amount, x=situation, fill = situation)) + 
    geom_bar(position="stack", stat="identity") + scale_y_continuous(labels = scales::comma) + theme( plot.title=element_text(hjust = 0.5, size = 10), axis.text.x = element_blank())
```

We can do a contrast analysis on crowdfunding and Graced, as well as liquidity coverages and series

```{r}
fcntrs  = og_data %>% mutate(situ_factor = factor(situation))
fcntrs
# get levels
levels(fcntrs$situ_factor)
```


```{r}
# graced and crowdfunding
hyp_gac = c(1, -1, 0, 0, 0, 0)
# liquidity and series
hyp_las = c(0, 0, 0, 1, 0, -1)
# validating summation
sum(hyp_gac)
sum(hyp_las)
# orthogonality
sum(hyp_gac * hyp_las)
```

```{r}
m = cbind(hyp_gac, hyp_las)
contrasts(fcntrs$situ_factor)<-m
save_lm = lm(raised_amount_usd ~ situ_factor, data = fcntrs) 
summary(save_lm)
```

High p-val = they do not differ
low p-val = they do differ


## Dilution
```{r}
dilu_sample = og_data %>% filter(!is.na(post_money_valuation_usd)) %>% mutate(investor_ownership = ifelse(investor_ownership > 1, 1, investor_ownership))
```

```{r}
ggplot(dilu_sample, aes(x = situation, y = investor_ownership, fill = situation)) + geom_boxplot() + theme( plot.title=element_text(hjust = 0.5, size = 10), axis.text.x = element_blank(), axis.ticks.x = element_blank())
```

```{r}
library(doBy)
mean_save = summaryBy(investor_ownership ~ situation, data = dilu_sample, 
            FUN = list(mean))
mean_save %>% arrange(desc(investor_ownership.mean))
```


```{r}
diluf_con  = dilu_sample %>% mutate(situ_factor = factor(situation))
# get levels
levels(diluf_con$situ_factor)
```

crowdfunding, graced, liquidity
series and publicity
```{r}
hyp_cg = c(1, -1, 0, 0, 0, 0)
# hyp_clq = c(1, 0, 0, -1, 0, 0)
#hyp_glq = c(0, 1, 0, -1, 0, 0)
hyp_sp = c(0, 0, 0, 0, 1, -1)

# validating ortogonality
sum(hyp_cg * hyp_sp)
m = cbind(hyp_cg, hyp_sp)
```

```{r}
contrasts(diluf_con$situ_factor)<-m
save_lm = lm(raised_amount_usd ~ situ_factor, data = diluf_con) 
summary(save_lm)
```
```{r}
hyp_clq = c(1, 0, 0, -1, 0, 0)
#hyp_glq = c(0, 1, 0, -1, 0, 0)
m = cbind(hyp_clq)
contrasts(diluf_con$situ_factor)<-m
save_lm = lm(raised_amount_usd ~ situ_factor, data = diluf_con) 
summary(save_lm)
```

```{r}
hyp_glq = c(0, 1, 0, -1, 0, 0)
#hyp_glq = c(0, 1, 0, -1, 0, 0)
m = cbind(hyp_glq)
contrasts(diluf_con$situ_factor)<-m
save_lm = lm(raised_amount_usd ~ situ_factor, data = diluf_con) 
summary(save_lm)
```


## Total amount of money per region

```{r}
sqldf("SELECT SUM(raised_amount_usd) amount_raised, ciaco, lon, lat
       FROM og_data
       GROUP BY ciaco, lon, lat") -> sum_ciaco
sum_ciaco
```

```{r}
max(sum_ciaco$raised_amount)
```


```{r}
my_pal = colorBin(c("#BEB8EB", "#345270", "#203244"), domain = 1:7, bins = 6)
pspal = c(my_pal(1), my_pal(2), my_pal(3), my_pal(4), my_pal(5), my_pal(6))

the_min = 0

start_rng = c(0, 10000001, 100000001, 1000000001, 10000000001, 25000000001)
end_rng = c(10000000, 100000000, 1000000000, 10000000000, 25000000000, max(sum_ciaco$amount_raised))

alt_pal = data.frame(start_rng, end_rng, pspal)
alt_pal = alt_pal %>% mutate(start_rng = as.numeric(start_rng), end_rng = as.numeric(end_rng))
labels = c("0 - 10,000,000", "10,000,001 - 100,000,000", "100,000,001 - 1,000,000,000", "1,000,000,001 - 10,000,000,000", "10,000,000,001 - 25,000,000,000", "25,000,000,000+")

alt_pal %>% mutate(range_str = labels) -> alt_pal

sqldf("SELECT sum_ciaco.*, alt_pal.*
       FROM sum_ciaco INNER JOIN alt_pal
                       ON sum_ciaco.amount_raised >= alt_pal.start_rng
                       AND sum_ciaco.amount_raised <= alt_pal.end_rng") -> with_pals
```

```{r}
leaflet() %>% addProviderTiles(providers$Stamen.TonerLite) %>% addCircleMarkers(data = with_pals, lng = ~lon, lat = ~lat,
                                               color = ~pspal, opacity = 0.65, radius = 10) %>% 
  addLegend(data = with_pals, colors = pspal, title = "Summation of amount raised per city (Aggregate)", labels = alt_pal$range_str)
```

